A Review of Neutron Imaging

### 2020-10-14 neutron-imaging/neutron.tex
WIP 14Oct2020

\section{Polarization based imaging}\label{s12}
\section{Imaging of biologically important structures}\label{s13}
\section{Conclusion}\label{s14}
\bibliography{neutron}
\bibliographystyle{plain}
\end{document}

>>>>

\section{Spin-echo based imaging}\label{s12}
Consider a beam of polarized nucleons (neutrons, protons, or nuclei with an odd
number of nucleons) passes through a region of homogenous magnetic field its
spin vector tilts with respect to the original direction because of Larmor
precession. When the nucleons emerge from the region, they all emerge with the
same tilt. However, as time goes by, different nucleons have a different angle
of tilt. This happens because of natural spin relaxation and due to 
inhomogeneities in the surroundings of the nucleons. If the nucleons are 
subjected to a field that flips the spin by $\pi$ then after a while all spins
that had dispersed due to inhomogeneities once again orient themselves together
creating an `echo'. The magnitude of the echo is not the same as that of the
original beam because of the natural spin relaxation. This is the principle
behind the 'spin-echo' phenomenon used in nuclear magnetic resonance 
spectroscopy and magnetic resonance imaging.

In the nuclear spin echo experiment this arrangement is enhanced with an 
additional region of uniform magnetic field, identical to the first one
\cite{mezei1972neutron}. When a polarized neutron enters the first region
of a uniform magnetic field, its spin vector tilts by an angle, say $\varphi$
radians. Different neutrons experience a different tilt depending on the 
time they spent in this region, which in turn depends on their velocity. Now
suppose that the neutron beam is made to pass through a target. Each neutron
will see a different local magnetic field in the target and will react to it
in its unique way. The beam of neutrons is further defocused because of these
inhomogeneities. It is then made to pass through a $\pi$ flipper. The 
defocusing that had occurred due to inhomogeneities gets a chance to correct
itself leading to a spin echo. A second region of a uniform magnetic field
brings all the spins to the direction parallel to the originally polarized
neutrons. The inelastic scattering of the neutrons in the target make some of
them lose more energy than others. The second region of homogeneous magnetic
field fails to bring such neutrons back to their original polarization state.
The difference in the direction of polarization creates the contrast for
neutron spin-echo imaging.

Neutron spin-echo imaging is used with small angle neutron scattering in the
investigation of soft matter. The latter technique provides information about
the structure. However, the mechanical properties depends on molecular 
mobilities and constraints of motion \cite{monkenbusch2007high}, where the
energy differences are of the order of $0.7 \mu$eV. Such small changes can be
resolved only through neutron spin-echo imaging.

\section{Imaging of biologically important structures}\label{s13}
Biological targets have an extremely rich mixture of molecules. A knowledge of
the presence of certain trace elements in the targets reveals important 
information about its functioning, health and pathology. Few imaging techniques
can accurately provide information about the elements. The chemical shift 
imaging in magnetic resonance imaging provides information at the molecular
level. It provides little information about the elements present. This is where
neutron imaging comes into the picture. When neutrons undergo an inelastic
scattering with the nuclei of the target, they nuclei get into an excited
state. They get back to their ground state after emitting a photon. We now 
have a detailed knowledge of the nuclear energy levels. By measuring the energy
of the emitted photon we can guess the nucleus, and thus the element, which
might have produced it. This is the principle behing the neutron stimulated
emission computed tomography (NSECT) imaging.
\section{Conclusion}\label{s14}
\bibliography{neutron}
\bibliographystyle{plain}
\end{document}
